---
title: "Coffee Survey Final Project EPI590R"
format: html
editor: visual
---

## Introduction to data

In October 2023, ["world champion barista" James Hoffmann](https://www.youtube.com/watch?v=bMOOQfeloH0) and [coffee company Cometeer](https://cometeer.com/pages/the-great-american-coffee-taste-test) held the "Great American Coffee Taste Test" on YouTube, during which viewers were asked to fill out a survey about 4 coffees they ordered from Cometeer for the tasting. [Data blogger Robert McKeon Aloe analyzed the data the following month](https://rmckeon.medium.com/great-american-coffee-taste-test-breakdown-7f3fdcc3c41d). This data set can be found under the 2024 folder in TidyTuesday.

## Read in the dataset 

```{r}
# read in data
coffee_survey <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2024/2024-05-14/coffee_survey.csv')

# data cleaning
library(tidyverse)
library(janitor)
library(here)
library(fs)

working_dir <- here::here("data", "2024", "2024-05-14")

url <- "https://bit.ly/gacttCSV"

coffee_survey_raw <- readr::read_csv(url)

# Grab the raw questions for the dictionary.
coffee_survey_raw |>
	colnames() |>
	cat(sep = "\n")

coffee_survey <- coffee_survey_raw |>
	janitor::clean_names() |>
	dplyr::select(
		submission_id,
		age = what_is_your_age,
		cups = how_many_cups_of_coffee_do_you_typically_drink_per_day,
		where_drink = where_do_you_typically_drink_coffee,
		brew = how_do_you_brew_coffee_at_home,
		brew_other = how_else_do_you_brew_coffee_at_home,
		purchase = on_the_go_where_do_you_typically_purchase_coffee,
		purchase_other = where_else_do_you_purchase_coffee,
		favorite = what_is_your_favorite_coffee_drink,
		favorite_specify = please_specify_what_your_favorite_coffee_drink_is,
		additions = do_you_usually_add_anything_to_your_coffee,
		additions_other = what_else_do_you_add_to_your_coffee,
		dairy = what_kind_of_dairy_do_you_add,
		sweetener = what_kind_of_sugar_or_sweetener_do_you_add,
		style = before_todays_tasting_which_of_the_following_best_described_what_kind_of_coffee_you_like,
		strength = how_strong_do_you_like_your_coffee,
		roast_level = what_roast_level_of_coffee_do_you_prefer,
		caffeine = how_much_caffeine_do_you_like_in_your_coffee,
		expertise = lastly_how_would_you_rate_your_own_coffee_expertise,
		starts_with("coffee"),
		prefer_abc = between_coffee_a_coffee_b_and_coffee_c_which_did_you_prefer,
		prefer_ad = between_coffee_a_and_coffee_d_which_did_you_prefer,
		prefer_overall = lastly_what_was_your_favorite_overall_coffee,
		wfh = do_you_work_from_home_or_in_person,
		total_spend = in_total_much_money_do_you_typically_spend_on_coffee_in_a_month,
		why_drink = why_do_you_drink_coffee,
		why_drink_other = other_reason_for_drinking_coffee,
		taste = do_you_like_the_taste_of_coffee,
		know_source = do_you_know_where_your_coffee_comes_from,
		most_paid = what_is_the_most_youve_ever_paid_for_a_cup_of_coffee,
		most_willing = what_is_the_most_youd_ever_be_willing_to_pay_for_a_cup_of_coffee,
		value_cafe = do_you_feel_like_you_re_getting_good_value_for_your_money_when_you_buy_coffee_at_a_cafe,
		spent_equipment = approximately_how_much_have_you_spent_on_coffee_equipment_in_the_past_5_years,
		value_equipment = do_you_feel_like_you_re_getting_good_value_for_your_money_with_regards_to_your_coffee_equipment,
		gender,
		gender_specify = gender_please_specify,
		education_level,
		ethnicity_race,
		ethnicity_race_specify = ethnicity_race_please_specify,
		employment_status,
		number_children = number_of_children,
		political_affiliation
	)

fs::dir_create(working_dir)

readr::write_csv(
	coffee_survey,
	here::here("data", "2024", "2024-05-14", "coffee_survey.csv")
)
```

## Average spending on coffee (function)

```{r}
avg_spend <- function(x) {
  n <- length(x)
  mean_val <- sum(x, na.rm = TRUE) / n
  return(mean_val)
}
```

## Table 1 (a {gtsummary} table of descriptive statistics)

```{r}

```

## Table 2 (Fit a regression and present well-formatted results from the regression)

```{r}
```

## Figure 1 

```{r}
```
